Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
tweak

A reader familiar with the type system for \origLang will notice that our type
system does not include types above the arrow in the function type, for giving
security bounds on side effects of the function, and the type does not include
effect labels for exceptions.  These are dropped as a result of the
simplifications we made in defining \langName, since there are no side effects
or exceptions in the language.

>>>>

A reader familiar with the type system for \origLang will notice that our type
system does not include labels above the arrow in the function type, which would
normally give security bounds on side effects of the function, nor does it
include effect labels for exceptions.  These are dropped as a result of the
simplifications we made in defining \langName, since there are no side effects
or exceptions in the language.
